\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
glitches + fixups

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ the set-valued function
\begin{eqnarray}
\partial_\epsilon f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x
\mapsto \{h \in \mathbb{R}^n | f(z) + \epsilon \ge f(x) + \langle h, z
- x\rangle \forall z \in X\}.
\end{eqnarray}
\end{definition}

@@

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
plans such that there exists dual vectors $p^*$ and $q^*$ and a
pertubation vector $v^*$ for which
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}
\label{thm:cool_notion}
\end{definition}

>>>>

\begin{definition}[$\epsilon$-subgradient \cite{he2013accelerating}]
Given a scalar $\epsilon > 0$ and a function $f:X \subseteq \mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ the set-valued function
\begin{eqnarray}
\partial_\epsilon f: X \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x
\mapsto \{h \in \mathbb{R}^n | f(z) + \epsilon \ge f(x) + \langle h, z
- x\rangle \forall z \in X\}.
\end{eqnarray}
\end{definition}

@@

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}
    \cite{he2013accelerating}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
plans such that there exists dual vectors $p^*$ and $q^*$ and a
pertubation vector $v^*$ for which
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}
\label{thm:cool_notion}
\end{definition}
